### 2016-03-30 Chapters/chap2/manuscript.tex
Finish first 3 chapts

In this chapter we focus here on the rates of triplet exchange between a naphthalene donor and a benzaldehyde acceptor linked by a variety of bridging units.
\begin{center}
\includegraphics[width=0.50\columnwidth]{Chapters/chap2/Scheme1}
\end{center}
Triplet energy exchange in these systems occurs via the through-space Dexter mechanism\cite{dexter1953theory}.
This is a short-ranged interaction involving the simultaneous exchange of two electrons between the
donor and acceptor moieties.
Systems such as these formed the basis of a series of experiments by  Closs and Miller\cite{miller1984intramolecular}
in which they verified the existence of the Marcus inverted regime
and serve as crucial benchmarks for testing new theoretical models for computing
energy and charge transfer rates\cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.

@@

A crucial part of our analysis is the identification of a subset of collective modes that contain
the electron-phonon couplings.  Moreover, we show that there exists a unique mode--the ``primary mode'',
determined via an iterative
approach, along which  the off-diagonal electron-phonon coupling is maximized.   Using only the primary mode
mode as input to our golden-rule rate expression, we obtain excellent
agreement (to within 2\% on average over   all of the donor-bridge-acceptor systems studied here)
when compared to an exact evaluation using all normal modes.   One can visualize the primary mode by projecting it on to the
nuclear displacement vectors and gain insight into the coupled electronic/nuclear motions that underlie an electronic
transition.   Our analysis also suggests that the primary  mode reflects the irreducible representations of the
donor and acceptor excited states.

>>>>

In this chapter we focus on the rates of triplet exchange between a naphthalene donor and a benzaldehyde acceptor linked by a variety of bridging units.
\begin{center}
\includegraphics[width=0.50\columnwidth]{Chapters/chap2/Scheme1}
\end{center}
Triplet energy exchange in these systems occurs via the through-space Dexter mechanism\cite{dexter1953theory}.
This is a short-ranged interaction involving the simultaneous exchange of two electrons between the
donor and acceptor moieties.
Systems such as these formed the basis of a series of experiments by  Closs and Miller\cite{miller1984intramolecular}
in which they verified the existence of the Marcus inverted regime
and serve as crucial benchmarks for testing new theoretical models for computing
energy and charge transfer rates\cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.

@@

A crucial part of our analysis is the identification of a subset of collective modes that contain
the electron-phonon couplings.  Moreover, we show that there exists a unique mode--the ``primary mode'',
determined via an iterative
approach, along which  the off-diagonal electron-phonon coupling is maximized.   Using only the primary mode
mode as input to our golden-rule rate expression, we obtain excellent
agreement (to within 2\% on average over   all of the donor-bridge-acceptor systems studied here)
when compared to an exact evaluation using all normal modes.   One can visualize the primary mode by projecting it on to the
nuclear displacement vectors and gain insight into the coupled electronic/nuclear motions that underlie an electronic
transition.   Our analysis also suggests that the primary  mode resembles certain  irreducible representations of the
donor and acceptor moieties. This is further explored in next chapter.
